---
title: "MyLeafletApp"
author: "TI"
date: "2022-06-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data
The data used is from: https://gist.github.com/Ewiseman/b251e5eaf70ca52a4b9b10dce9e635a4.
I created a new variable called `diff` (Difficulty) that is based on 3 quantiles of the percentage of black acres on the resort. If the resort is in the top quantile, it is a "black" difficulty, middle is "blue", and bottom is "green".
```{r, message=FALSE}
library(leaflet)
library(readr)
library(Hmisc)

ski_resorts <- read_csv("./skiresorts.csv") %>% na.omit(.)
cuts <- cut2(ski_resorts$black_percent, g = 3)
ski_resorts$diff <- cuts
levels(ski_resorts$diff) <- c("green", "blue", "black")
head(ski_resorts)
```


# Ski Resorts of the United States
The size of the circle represents the overall footprint of the resort, scaled from the original unit of measure (Acres)). Clicking on the circle will bring up the resort name.
```{r, message = FALSE, fig.align='center'}
ski_resorts %>%
    leaflet() %>% 
    addTiles() %>%
    addCircleMarkers(
        weight = 3, 
        radius = ski_resorts$acres / 750, 
        popup = ski_resorts$resort_name,
        color = ski_resorts$diff
    )

```

*There's a few errors in the original data set! (Ski resort in the south pacific and off the coast of Panama??)*